CTest Integration of Sikuli Automated GUI Testing

### 2011-06-10 Documentation/Article.tex
More edits and \emph{} to Example section

Figure 1 shows the Sikuli-IDE for version 0.10.2.  On the left-hand side menu is a list
of commonly used Sikuli commands like find(), click(), and type().  The picture of
the camera within the parentheses indicates the screenshot input variable.  Clicking
on any of these menu functions will automatically set up the Sikuli screen shot mode, whereby
the Sikuli-IDE disappears and what is on the screen at that moment is available to capture 
by selecting a rectangular region of interest.  The function will then appear in the scripting domain
with the snap shot in parentheses as shown in Figure 1.  The user may also type in the function
and invoke the screen shot mode by clicking on the camera in the top menu or by using a
keyboard shortcut. The simple Sikuli script example in Figure 1 will open gedit Text Editor, type a message,
and save the file. (see Figure~\ref{fig:SimpleExample}).

@@

This breakdown of modes and actions lends itself to a nested for-loop scripting approach. In addition to representing the modes and actions
as the vectors Toolbar and Mouse, respectively, we've included the different data set plots in the vector ViewRegion.
These images represent the xy, xz, yz, and xyz views of zebrafish microscopy data taken in the Megason Lab.  After capturing
these images we can then use them to locate their initial pixel coordinates within the GoFigure2 GUI using the \emph{find}() function.  These points become 
our reference positions to calculate directional movement.  For example, when testing the pan mode, we mark the initial position of each image,
use the \emph{mouseMove}() function to a chosen location, and then use \emph{find}() to obtain the new coordinates.  We can then assert if the image panned as it should have.
Similarly for zoom, we can first find the area of the image and then find the area of the zoomed in image.  To test the result when the user clicks 
in a certain mode, we've made use of Sikuli's \emph{assert exists}() function to ascertain the existence of our
desired results   (see Figure~\ref{fig:Gofigure2Example}).

>>>>

Figure 1 shows the Sikuli-IDE for version 0.10.2.  On the left-hand side menu is a list
of commonly used Sikuli commands like  \emph{find}(),  \emph{click}(), and  \emph{type}().  The picture of
the camera within the parentheses indicates the screenshot input variable.  Clicking
on any of these menu functions will automatically set up the Sikuli screen shot mode, whereby
the Sikuli-IDE disappears and what is on the screen at that moment is available to capture 
by selecting a rectangular region of interest.  The function will then appear in the scripting domain
with the snap shot in parentheses as shown in Figure 1.  The user may also type in the function
and invoke the screen shot mode by clicking on the camera in the top menu or by using a
keyboard shortcut. The simple Sikuli script example in Figure 1 will open gedit Text Editor, type a message,
and save the file. (see Figure~\ref{fig:SimpleExample}).

@@

This breakdown of modes and actions lends itself to a nested for-loop scripting approach. By representing
these variables as a vector the software developers can easily add new modes or actions to each list to be tested, when
the software is updated. Similarly, the tester can easily replace any of the screenshot images with images of updated
GUI icons.\\

In addition to representing the modes and actions
as the vectors Toolbar and Mouse, respectively, we've included the different data set plots in the vector ViewRegion.  
These images represent the  \emph{xy-},  \emph{xz-},  \emph{yz-}, and  \emph{xyz-}views of zebrafish microscopy data taken in the Megason Lab.  After capturing
these images we can then use them to locate their initial pixel coordinates within the GoFigure2 GUI using the \emph{find}() function.  These points become 
our reference positions to calculate directional movement.  For example, when testing the pan mode, we mark the initial position of each image,
use the \emph{mouseMove}() function to a chosen location, and then use \emph{find}() to obtain the new coordinates.  We can then assert if the image panned as it should have.
Similarly for zoom, we can first find the area of the image and then find the area of the zoomed in image.  To test the result when the user clicks 
in a certain mode, we've made use of Sikuli's \emph{assert exists}() function to ascertain the existence of our
desired results   (see Figure~\ref{fig:Gofigure2Example}).\\

This one GUI test is then combined with other GoFigure2 tests in succession and the Sikuli Unit Testing CTest integration will identify
which tests pass and which fail and when. Many of the units need to be tested in a certain order.  For example, in order to test the Toolbar modes
on the data sets, one first needs to test the software's data import functionality.
